### 2016-05-03 ch06-concl/conclusions.tex
Finished conclusions

\section{Results of this Research}
\TODO{general introduction, claim the title, reaffirm the structure of the book}

>>>>

In this thesis, user-friendly system identification methods have been developed.
These methods require little to no user interaction and are designed such that the method work for a broad range of systems.
As such, many of the obtained improvements can be obtained without bothering the user for further information and tuning.
Throughout this dissertation, so-called `Guidelines' have been scattered that offer a bird's eye view of the work from a practical point of view.
In the following sections, the main results of this work are summarized and perspectives are sketched for further (and ongoing) research paths.

\section{Results of this Research}
